Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - WiP}}

### 2014-12-18 Paper.tex
Specify Blooms formally.

We assert $R_u$, the cumulative gas used is a positive integer and that the logs Bloom, $R_b$, is a hash of size 64 bytes:
\begin{equation}
R_u \in \mathbb{P} \quad \wedge \quad R_b \in \mathbb{B}_{32}
\end{equation}

@@

>>>>

We assert $R_u$, the cumulative gas used is a positive integer and that the logs Bloom, $R_b$, is a hash of size 512 bits (64 bytes):
\begin{equation}
R_u \in \mathbb{P} \quad \wedge \quad R_b \in \mathbb{B}_{64}
\end{equation}

@@

We define the Bloom filter function, $M$, to reduce a log entry include a single 64-byte hash:
\begin{equation}
M(O) \equiv h: m(O_a) \; \vee \; \bigvee_{t \in O_\mathbf{t}} ( M_{3:512}(t) )
\end{equation}

where $M_{3:512}$ is a specialised Bloom filter that sets three bits out of 512, given an arbitrary byte series. It does this through taking the low-order 9 bits of each of the first three pairs of bytes in a Keccak-256 hash of the byte series. Formally:
\begin{eqnarray}
M_{3:512}(\mathbf{x}: \mathbf{x} \in \mathbb{B}) & \equiv & \mathbf{y}: \mathbf{y} \in \mathbb{B}_{64} \quad \text{where:}\\
\mathbf{y} & = & (0, 0, ..., 0) \quad \text{except:}\\
\forall_{i \in \{0, 2, 4\}}&:& \mathcal{B}_{m(\mathbf{x}, i)}(\mathbf{y}) = 1\\
m(\mathbf{x}, i) &\equiv& \mathtt{\tiny KEC}(\mathbf{x})[i, i + 1] \bmod 512
\end{eqnarray}

where $\mathcal{B}$ is the bit reference function such that $\mathcal{B}_j(\mathbf{x})$ equals the bit of index $j$ (indexed from 0) in the byte array $\mathbf{x}$.
